Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-15 paper/main.tex
added comment about no increase in velocity dispersion

\author{Salvatore Ferrone
       \inst{1,2}
         \and
       Marco Montuori\inst{2}
       \and
       Paola Di Matteo\inst{1}
       \and
       Alessandra Mastrobuono-Battisti \inst{3}
       \and 
       Misha Haywood \inst{1}
       \and
       Rodrigo Ibata \inst{4}
       \and 
       Paolo Bianchini \inst{4}
       \and
       Sergey Khopserskov \inst{5}
       \and
       Nicolas Leclerc \inst{1}
       \and 
       Clement Hottier \inst{1}
       \and 
       Eliot Stein  \inst{1}
       \and
       David Valls-Gabaud \inst{1}
       \and
       Owain N. Snaith \inst{6}
       }

@@

      The procedure described so far has been repeated 50 times, each time generating a new set of initial conditions, given the uncertainties on proper motions, line-of-sight velocities, distances to the Sun, and masses, of all clusters, as reported in the Baumgardt catalog. We handle these uncertainties  through a Monte-Carlo approach, by sampling them with Gaussian distribution, and by taking into account the covariance term between the proper motions. For the first simulation, we use the most probable values for the initial conditions.

@@

    The analysis presented in Fig.~\ref{fig:decomposition} has been repeated for the whole set of simulations, and is reported in Appendix~\ref{sec:gallery_of_gaps} for completeness. From this analysis we can derive a statistical view of: 1) the number of gaps generated on Pal~5 stream by the whole system of Galactic globular clusters; 2) the clusters which generated these gaps and the time history of these perturbations. From this, we can then quantify: 3) the properties of the perturbers (their masses, sizes and their orbital parameters) as well as 4) the impact geometry of the encounters, which allows us to understand which encounters are more favorable to generate gaps in Pal~5 stream. In the following, we will present results of this analysis, by starting from addressing points 1) and 2).

>>>>

\author{Salvatore Ferrone
       \inst{1,2}
         \and
       Marco Montuori\inst{2}
       \and
       Paola Di Matteo\inst{1}
       \and
       Alessandra Mastrobuono-Battisti \inst{3}
       \and 
       Misha Haywood \inst{1}
       \and
       Rodrigo Ibata \inst{4}
       \and 
       Paolo Bianchini \inst{4}
       \and
       Sergey Khoperskov \inst{5}
       \and
       Nicolas Leclerc \inst{1}
       \and 
       Clement Hottier \inst{1}
       \and 
       Eliot Stein  \inst{1}
       \and
       David Valls-Gabaud \inst{1}
       \and
       Owain N. Snaith \inst{6}
       }

@@

        The procedure described so far has been repeated 50 times, each time generating a new set of initial conditions, given the uncertainties on proper motions, line-of-sight velocities, distances to the Sun, and masses, of all clusters, as reported in the Baumgardt catalog. We handle these uncertainties through a Monte-Carlo approach, by sampling them with Gaussian distribution, and by taking into account the covariance term between the proper motions. For the first simulation, we use the most probable values for the initial conditions. The uncertainties are sample for all globular clusters. Additionally, for each re-sampling of Palomar~5's mass, we also resample the distribution of the 100,000 star-particles.

@@

    The analysis presented in Fig.~\ref{fig:decomposition} has been repeated for the whole set of simulations, and is reported in Appendix~\ref{sec:gallery_of_gaps} for completeness. For all of the streams, morphologically speaking, the only changes appear to be the existence of gaps or not. We do not observe a thickening of the streams due to an increased velocity dispersion.

    From this analysis we can derive a statistical view of: 1) the number of gaps generated on Pal~5 stream by the whole system of Galactic globular clusters; 2) the clusters which generated these gaps and the time history of these perturbations. From this, we can then quantify: 3) the properties of the perturbers (their masses, sizes and their orbital parameters) as well as 4) the impact geometry of the encounters, which allows us to understand which encounters are more favorable to generate gaps in Pal~5 stream. In the following, we will present results of this analysis, by starting from addressing points 1) and 2).
